Supplementary appendix

### 2019-07-15 paper3_APPENDIX_revision_01.Rmd
Add files via upload

---
title: "Supplementary appendix"
author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
date: " "
output:
  html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
  word_document: default
link-citations: yes
bibliography: phd_paper_2.bib
urlcolor: blue
---

@@

```{r , include=FALSE, echo=FALSE}
#load("C:/SAAR/UNIVERSITY/R/SVIVA/.RData")

@@

SVIVA1_01 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/SVIVA1_01.csv")
CELEBS_00 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/CELEBS.csv")

SVIVA2_01 = SVIVA2_01 %>%  
mutate(AREA_center = Recode(AREA,"0=1;1=0"))

SVIVA2_01_haifa = filter(SVIVA2_01,AREA==1)
SVIVA2_01_center = filter(SVIVA2_01,AREA==0)

@@

```{r , include=FALSE, echo=FALSE}
library(tidyverse)
library(sjPlot)
library(stargazer)
```

@@

# Contents:

@@

# 1. Supplementary information about the symbolic elements

@@

# 2. Manipulation and validity checks

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
set_theme("scatterw")

sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_recognize,
        geom.size = 0.9,
        ylim=c(0,155),
        axis.title="",
        title = "Real logo")

sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_recognize,
        geom.size = 0.9,
        ylim=c(0,155),
        axis.title="",
        title = "Fake logo")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
set_theme("scatterw")

sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,160),
        axis.title="",
        title = "Real logo")

sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,160),
        axis.title="",
       title = "Fake logo")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real celeb (Tal Friedman)")

sjp.frq(CELEBS_00$air_fake_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Unfamiliar model")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real celeb (Ido Rosenblum)")

sjp.frq(CELEBS_00$waste_fake_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        xlim=c(0,110),
        axis.title="",
        title = "Unfamiliar model")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Fake campaign")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Fake campaign")

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_positive_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_positive_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Fake campaign")

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_positive_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_positive_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Fake campaign")

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_negative_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,80),xlim=c(0.5,7.5),
        axis.title="",
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_negative_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,80),
        axis.title="",
        title = "Fake campaign")

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_negative_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,80),xlim=c(0.5,7.5),
        axis.title="",
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_negative_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,80),
        axis.title="",
        title = "Fake campaign")

@@

The comparison between the two areas is based on the assumption that the Air-pollution policy is perceived as more personally relevant by Haifa-Bay subjects, whereas the recycling policy is perceived as equally relevant by both groups. To test that assumption, I relied on the following question, which was included in the survey, regarding both policy plans:

"To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa-Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").

The air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents. As for the recycling policy, it is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them. The distribution of the perceived personal relevance variable of the two policies, across the two areas, is displayed in the following figures.

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(filter(SVIVA2_01_comb,AREA==0)$RELEVANCE_air_obs,
        type="hist",
        show.mean = T,
        ylim=c(0,600),xlim=c(0.5,7.5),
        axis.title="",
        title = "Center")

sjp.frq(filter(SVIVA2_01_comb,AREA==1)$RELEVANCE_air_obs,
        type="hist",
        show.mean = T,
        ylim=c(0,600),xlim=c(0.5,7.5),
        axis.title="",
        title = "Haifa-bay")

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(filter(SVIVA2_01_comb,AREA==0)$RELEVANCE_waste_obs,
        type="hist",
        show.mean = T,
        ylim=c(0,600),xlim=c(0.5,7.5),
        axis.title="",
        title = "Center")

sjp.frq(filter(SVIVA2_01_comb,AREA==1)$RELEVANCE_waste_obs,
        type="hist",
        show.mean = T,
        ylim=c(0,600),xlim=c(0.5,7.5),
        axis.title="",
        title = "Haifa-bay")

Moreover, Participants in the relevance treatment group were asked to describe the most salient environmental issue in their area of residence. Indeed, most of the Haifa-Bay subjects regarded in their responses to the air-pollution generated from the industrial area, and many of them linked it to higher morbidity rates in the area. Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, whereas relatively few of them mentioned air-pollution as a prominent environmental concern in their area.

@@

# 3. Power estimations

@@

# 4. Summary statistics

@@

# X raw experimental results

```{r}
t3.comb <- rbind(t3.haifa,
                 t3.center) %>%
  filter(str_detect(variable,"policy")==T) %>%
  select(-starts_with("statistic")) %>%

@@

t11.comb <- t11.all %>% 
  cbind(t11.symbol  %>% 
          select(-variable)) %>% 
  cbind(t11.info %>% 
          select(-variable)) %>%
  cbind(t1.relevance %>% 
          select(-variable)) %>% 
  mutate(variable = c("Air-pollution policy","Recycling policy"))

@@

t11.all <- rbind(
  t11.comb,
  t13.haifa,
  t13.center
) %>% 
  mutate(area = rep(c("All","Haifa-Bay","Center"),each=2)) %>% 
  select(area,1:9)

@@

```{r}
t11.all %>% 
  kable(col.names = c("Area",
                      "Policy",
                    "All sample",
                    "No symbols",
                    "Fake symbols",
                    "Real symbols",
                    "Strong Air-pollution (Weak recycling)",
                    "Weak air-pollution (Strong recycling)",
                    "Treatment",
                    "Control"))%>%
  kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left",
                font_size = 9) %>%
  add_header_above(c(" " = 3, 
                     "Symbols groups" = 3,  
                     "Information groups" = 2, 
                     "Relevance groups" = 2))  %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

# 5. Supplementary analyses

@@

# 6. English translation of the survey experiment

>>>>

---
title: "Supplementary appendix"
author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
date: " "
output:
  html_document:
    theme: flatly
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
  word_document: default
link-citations: yes
bibliography: phd_paper_2.bib
urlcolor: blue
---

@@

```{r , include=FALSE, echo=FALSE}
load("C:/SAAR/UNIVERSITY/R/SVIVA/.RData")

@@

SVIVA1_01 <- read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/SVIVA1_01.csv")
CELEBS_00 <- read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/CELEBS.csv")
CITIES_table <- read_csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/CITIES_table.csv")
CITIES_table[is.na(CITIES_table)] <- ""

@@

```{r , include=FALSE, echo=FALSE}
library(knitr)
library(tidyverse)
library(stargazer)
library(car)
library(broom)
library(kableExtra)
library(sjPlot)
library(ggthemes)
library(ggpubr)
```

@@

**Contents:**

@@

# Properties of the selected cities

```{r, echo=FALSE,warning=FALSE,message=FALSE}
CITIES_table %>% 
  kable(col.names = c("Area",
                      "City",
                    "Population",
                    "Socio-economic rank (10=highest)",
                    "Average income per employee (NIS)",
                    "GINI",
                    "% children (0-14)",
                    "N participants in analytical sample"))%>%
  kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left",
                font_size = 9) %>%
  collapse_rows(columns = 1, valign = "top")
```
<font size="0.5">

Notes:
Data for all cities, except for Qiryat-Hayiim, is retrived from the Central Bureau of Statistics data file of local authorities in Israel of 2015. Qiryat-Hayiim is considered, formally, a neighborhood within the jurisdiction of Haifa, although it is geographically seperated from the rest of the city. Therefore, it is included in the official statistical data within Haifa. The population of Qiryat-Hayiim is based on a document of statistical data for neighborhoods in Haifa for 2015, retrived from the website of the municipality of Haifa.

# Supplementary information about the symbolic elements

@@

# Manipulation and validity checks

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}

set_theme(
  base=theme_tufte(),
  geom.outline.size = 0.01,
  geom.outline.color = "white", 
  geom.label.size = 3,
  geom.label.color = "grey50")

p1 <- sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_recognize,
        geom.size = 0.75,
        ylim=c(0,155),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real logo")

p2 <- sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_recognize,
        geom.size = 0.75,
        ylim=c(0,155),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake logo")

ggarrange(p1,p2,
          ncol = 2,nrow = 1) 
```

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}

p1 <- sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,160),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real logo")

p2 <- sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,160),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
       title = "Fake logo")

ggarrange(p1,p2,
          ncol = 2,nrow = 1) 
```

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
p1 <- sjp.frq(CELEBS_00$air_real_person_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real celeb (Tal Friedman)")

p2 <- sjp.frq(CELEBS_00$air_fake_person_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Unfamiliar model")

ggarrange(p1,p2,
          ncol = 2,nrow = 1)

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
p1 <- sjp.frq(CELEBS_00$waste_real_person_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real celeb (Ido Rosenblum)")

p2 <- sjp.frq(CELEBS_00$waste_fake_person_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        xlim=c(0,110),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Unfamiliar model")

ggarrange(p1,p2,
          ncol = 2,nrow = 1)

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}

p1 <- sjp.frq(CELEBS_00$air_real_ad_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (starting to think green)")

p2 <- sjp.frq(CELEBS_00$air_fake_ad_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")

ggarrange(p1,p2,
          ncol = 2,nrow = 1) 
```

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
p1 <- sjp.frq(CELEBS_00$waste_real_ad_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (reusable bags)")

p2 <- sjp.frq(CELEBS_00$waste_fake_ad_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")

ggarrange(p1,p2,
          ncol = 2,nrow = 1) 
```

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
p1 <- sjp.frq(CELEBS_00$air_real_positive_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (starting to think green)")

p2 <- sjp.frq(CELEBS_00$air_fake_positive_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")

ggarrange(p1,p2,
          ncol = 2,nrow = 1)
```

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
p1 <- sjp.frq(CELEBS_00$waste_real_positive_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (reusable bags)")

p2 <- sjp.frq(CELEBS_00$waste_fake_positive_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")

ggarrange(p1,p2,
          ncol = 2,nrow = 1)
```

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
p1 <- sjp.frq(CELEBS_00$air_real_negative_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,80),xlim=c(0.5,7.5),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (starting to think green)")

p2 <- sjp.frq(CELEBS_00$air_fake_negative_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,80),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")

ggarrange(p1,p2,
          ncol = 2,nrow = 1)

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
p1 <- sjp.frq(CELEBS_00$waste_real_negative_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,80),xlim=c(0.5,7.5),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (reusable bags)")

p2 <- sjp.frq(CELEBS_00$waste_fake_negative_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,80),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")

ggarrange(p1,p2,
          ncol = 2,nrow = 1)
```

@@

@@

# Power estimations

@@

# Summary statistics

@@

# Raw experimental results

```{r, echo=FALSE,warning=FALSE,message=FALSE}
t3.comb <- rbind(t3.haifa,
                 t3.center) %>%
  filter(str_detect(variable,"policy")==T) %>%
  select(-starts_with("statistic")) %>%

@@

t11.comb <- t11.all %>% 
  cbind(t11.symbol  %>% 
          select(-variable)) %>% 
  cbind(t11.info %>% 
          select(-variable)) %>%
  cbind(t11.relevance %>% 
          select(-variable)) %>% 
  mutate(variable = c("Air-pollution policy","Recycling policy"))

@@

t11.all <- rbind(
  t11.comb,
  t13.haifa,
  t13.center
) %>% 
  mutate(area = rep(c("All","Haifa-Bay","Center"),each=2)) %>% 
  select(area,1:9) %>% 
  mutate(variable = variable %>% str_remove(" policy"))

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE}
t11.all %>% 
  kable(col.names = c("Area",
                      "Policy",
                    "All sample",
                    "No symbols",
                    "Fake symbols",
                    "Real symbols",
                    "Strong Air-pollution (Weak recycling)",
                    "Weak air-pollution (Strong recycling)",
                    "Treatment",
                    "Control"))%>%
  kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left",
                font_size = 9) %>%
  add_header_above(c(" " = 3, 
                     "Symbols groups" = 3,  
                     "Information groups" = 2, 
                     "Relevance groups" = 2))  %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

# Supplementary analyses

- models for relevance for center (air-pollution).

mod_relevance_null.a = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb %>% filter(AREA_center==1))
mod_relevance_1.1.a = update(mod_relevance_null.a,. ~ .+
                             SYMBOL_t+
                   INFORMATION_weak+
                   RELEVANCE_exp)
mod_relevance_1.2.a = update(mod_relevance_1.1.a,. ~ .+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
mod_relevance_1.3.a = update(mod_relevance_1.2.a,. ~ .+
                   GENDER+
                   AGE+
                   GOV_TRUST+
                   IDEOLOGY+
                   EDUCATION+
                   INCOME+
                   CHILDREN_young)

mod_relevance_1.4.a = update(mod_relevance_1.2.a,. ~ .,data=SVIVA2_01_comb.center_air_first)

## Adjust standard errors & F statistic
mod_relevance_1.1.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.1.a, type = "HC1")))
mod_relevance_1.1.a.wald_results <- waldtest(mod_relevance_1.1.a, vcov = vcovHC(mod_relevance_1.1.a, type = "HC1"))

mod_relevance_1.2.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.2.a, type = "HC1")))
mod_relevance_1.2.a.wald_results <- waldtest(mod_relevance_1.2.a, vcov = vcovHC(mod_relevance_1.2, type = "HC1"))

mod_relevance_1.3.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.3.a, type = "HC1")))
mod_relevance_1.3.a.wald_results <- waldtest(mod_relevance_1.3.a, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))

mod_relevance_1.4.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.4.a, type = "HC1")))
mod_relevance_1.4.a.wald_results <- waldtest(mod_relevance_1.4.a, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
control.vars <- c("GENDER",
                  "AGE",
                  "GOV_TRUST",
                   "IDEOLOGY",
                   "EDUCATION",
                   "INCOME",
                   "CHILDREN_young")

stargazer(mod_relevance_1.1.a,mod_relevance_null.a,
          mod_relevance_1.2.a,mod_relevance_null.a,
          mod_relevance_1.3.a, mod_relevance_null.a,
          mod_relevance_1.4.a, mod_relevance_null.a,
          type = "html",
          se  = list(mod_relevance_1.1.a.robust_se,NULL,
                     mod_relevance_1.2.a.robust_se,NULL,
                     mod_relevance_1.3.a.robust_se,NULL,
                     mod_relevance_1.4.a.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("(3.",1:4,")"),
          column.separate = c(2,2,2),
          dep.var.labels="Trust in air-pollution policy",
          omit = control.vars,
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Relevance treatment",
                             "Relevance treatment x Real symbols",
                             "Relevance treatment x Fake symbols",
                             "Relevance treatment x Weak Information"),
          p.auto = F,
          add.lines = list(
                           c("Controls","No","","No","","Yes","","No",""),
                           c("F Statistic", 
                             mod_relevance_1.1.a.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_1.2.a.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_1.3.a.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_1.4.a.wald_results[2,3] %>% round(2),NA)),
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients. Robust standard errors are in parentheses and *p-values* (two-tailed) are reported. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)
```

- Models for relevance for both groups for recycling. 
- replicating all regression tables for upfilterred sample.

@@

# English translation of the survey experiment
